`SimSurvey`: an `R` package for comparing the design and analysis of fisheries surveys by simulating spatially-correlated fish stocks

### 2020-02-05 analysis/paper/sim_survey_paper.Rmd
Start revision given latest reveiw; add paragraph to intro

>>>>

Good survey design is a critical prerequisite for obtaining accurate and precise estimates of a population of interest. The need for sound sampling techniques is as relevant today it was in the 1930's when much of the theory and principles behind the collection of scientific data were laid by statisticians such as R.A. Fisher and Jerzy Neyman [@fienberg1996]. Then and now, we are experiencing a period of increasing human activity and robust methods are required to detect the impacts of our actions on the natural world [@nichols2006]. Survey quality is especially important for conservation-oriented science as monitoring data are used to identify species at risk of extinction [@martin2007], to assess the efficacy of recovery plans [@campbell2002], and to determine precautionary levels of exploitation [@sutherland2001]. Though large-scale surveys require careful planning and are costly to implement [@reynolds2011], they are not easily replaced by other approaches. For instance, numerous attempts to infer population size using catch per unit effort (CPUE) data from commercial or recreational fisheries have been froth with bias because CPUE and abundance are rarely proportional [@harley2001; @maunder2006]. As such, fisheries-independent surveys have become the preferred source of information as designs with a solid basis in sampling theory can be imposed.

<!-- consider keeping last sentence above general then suegue in the below paragraph to fisheries surveys somehow... -->
